Supplemental Material for submission ``Do Objects in Real-World Images Have a Canonical Name?''

### 2019-05-21 papers/EMNLP2019/modeling.tex
modeling section free for revision

		all            &               68.7 &                 76.8 &                   94.8 &            0.9 &            20.7 &              52.6 &                92.4 &         1.2 &             63.5 &               73.1 &                 92.5 &          1.0 \\ \\

@@

\subsection{Experimental Setup}
\textbf{STILL TO BE DONE: Model, Data}
\paragraph{Classification model}
We used \citeauthor{anderson2018updown}'s \citeyear{anderson2018updown} bottom-up attention model (\textit{Bottom-up} henceforth)\footnote{The features code and data is available at \url{https://github.com/peteanderson80/bottom-up-attention}}. 
It uses Faster R-CNN in conjunction with the ResNet-101 CNN and was pretrained on object and attribute annotations from VisualGenome (after initialization with pretrained ImageNet model).
\iffalse
"To pretrain the bottom-up attention model, we first initialize Faster R-CNN with ResNet-101 pretrained for classification on ImageNet [35]. We then train on Visual
Genome [21] data. To aid the learning of good feature
representations, we add an additional training output for
predicting attribute classes (in addition to object classes).
To predict attributes for region i, we concatenate the mean
pooled convolutional feature vi with a learned embedding
of the ground-truth object class, and feed this into an additional output layer defining a softmax distribution over each
attribute class plus a ‘no attributes’ class.
The original Faster R-CNN multi-task loss function contains four components, defined over the classification and
bounding box regression outputs for both the RPN and the
final object class proposals respectively. We retain these
components and add an additional multi-class loss component to train the attribute predictor"
\fi

\paragraph{Data}
\begin{itemize}
	\item We use the softmax distribution for the VG object names, and ignore the distribution over attributes. 
	\item The authors manually cleaned the set of object names to remove those with poor detection performance.
	\item Set of classes: 1,600 object names
	Overlapping classes, such as \textsl{person} and \textsl{guy}, were not merged to single classes. (For those cases, we therefore would expect that evaluating the model output on our set of names per instance to yield higher detection accuracy. )
	\item Image set and vocabulary: $346$~name types are not in MN, i.e., our vocabulary (MN--VG) contains $1,254$~names. 
	We filtered out those images whose VG name was not found in MN--VG, which resulted in $24,585$~instances (note that of those $22,304$~images were also part of the training data of bottom-up)
\end{itemize}

\paragraph{Evaluation measures}
Model effectiveness is assessed in both, the commonly used single-ground-truth setting and in a multi-label setting. 
In the former, for each instance, we compare the model's top prediction to its VG name and to the top response in MN, respectively, and report the average accuracy across all instances (\textit{=VG} and \textit{=MN-1}, respectively).
In the multi-label setting, we report the average accuracy of the top prediction to match any of the responses in MN. 
To assess the model's ability to account for human naming variations of MN instances, including the likelihood of names being produced for an instance, we treat the model's softmax output~$S$ as a probability distribution and compare it to the probability distribution~$M$ over the MN responses (estimated by normalizing the name counts). 
We report the average Kullback-Leibler divergence~$\mathrm{D_{KL}}(M||S)$ \cite{kullback1951information}.

>>>>

		\midrule \vspace{.6ex}
		all            &               68.7 &                 76.8 &                   94.8 &            0.9 &            20.7 &              52.6 &                92.4 &         1.2 &             63.5 &               73.1 &                 92.5 &          1.0 \\ 

@@

\subsection{Experimental Setup}
\paragraph{Classification model}
To obtain object label predictions we used \citeauthor{anderson2018updown}'s \citeyear{anderson2018updown} bottom-up attention model (\textit{Bottom-up} henceforth)\footnote{The features code and data is available at \url{https://github.com/peteanderson80/bottom-up-attention}}. 
It's feature vectors were used to train state-of-the-art image captioning and visual question answering models. 
The model is based on the object detection method Faster R-CNN \cite{fasterrcnn2015}, which the authors  initialized with ResNet-101 \cite{he2016deep} features (pretrained on ImageNet) to then train it on \vgenome (\vg).\footnote{Bottom-up is trained with an additional output over attributes, but we only use the object class prediction layer.} 
%
\iffalse
"To pretrain the bottom-up attention model, we first initialize Faster R-CNN with ResNet-101 pretrained for classification on ImageNet [35]. We then train on Visual
Genome [21] data. To aid the learning of good feature
representations, we add an additional training output for
predicting attribute classes (in addition to object classes).
To predict attributes for region i, we concatenate the mean
pooled convolutional feature vi with a learned embedding
of the ground-truth object class, and feed this into an additional output layer defining a softmax distribution over each
attribute class plus a ‘no attributes’ class.
The original Faster R-CNN multi-task loss function contains four components, defined over the classification and
bounding box regression outputs for both the RPN and the
final object class proposals respectively. We retain these
components and add an additional multi-class loss component to train the attribute predictor"
\fi

\paragraph{Data}
Bottom-up was trained on a set of $1,600$\ object names (the authors manually removed names with poor a detection performance from the original set). 
Overlapping classes, such as \textsl{person} and \textsl{guy}, were not merged to single classes which is in line with the data structure of MN. 
%(For those cases, we would expect that evaluating the model output on our set of names per instance to yield higher detection accuracy.)
Despite the much larger vocabulary of MN ($XX$\ name types), $346$~types are not in MN, which we removed, resulting in a final vocabulary (\mbox{MN$\cap$VG}) of $1,254$~names. 
Similarly, we filtered out the images of MN whose \vg name was not in \mbox{MN$\cap$VG}, which resulted in $24,585$~instances (note that of those, $22,304$~images were also part of Bottom-up's training data).

\paragraph{Evaluation Procedure}
We apply Bottom-up to each image and extracted the distribution~$S$ over object labels from the final softmax layer output for the ground-truth bounding box of the target object.

Model effectiveness is assessed in both, the commonly used single-ground-truth setting and in a multi-label setting. 
In the former, for each instance, we compare the model's top prediction (the object label with the highest score in\ $S$) to its VG name and to the top response in MN, respectively, and report the average accuracy across all instances (\textit{=VG} and \textit{=MN-1}, respectively).
In the multi-label setting, we report the average accuracy of the top prediction to match any of the responses in MN. 
To assess the model's ability to account for human naming variations of MN instances, including the likelihood of names being produced for an instance, we treat\ $S$ as a probability distribution and compare it to the probability distribution~$M$ over the MN responses (estimated by normalizing the name counts). 
We report the average Kullback-Leibler divergence~$\mathrm{D_{KL}}(M||S)$ \cite{kullback1951information}.
